### 2023-12-02 main.tex
''

Our strategy to solve for the non-equilibrium steady state is of a probabilistic nature and relies on the use of {\em duality} \cite{schutzSandow}. Starting from the pioneering work of Kipnis, Marchiorio and Presutti \cite{KMP}, this approach
has been substantially developed in recent years to study stochastic processes in the boundary-driven set-up \cite{giardina2009duality,carinci2013duality}.
The boundary-driven process is mapped to a dual process with absorbing extra sites and the problem of describing the stationary state of the original system
is reduced to the problem of computing the absorption probabilities of the dual particles.
{\color{red} Say that for a  general graph with boundaries attached to any site, this is a difficult task. }
% However,  for the case of integrable systems they can be computed exactly in closed-form.

@@

    \bm{\xi}=\left(\xi_{1}^{x},\ldots,\xi_{N}^{x}\right)\otimes (\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)} )_{x\in V}
\todo{OK? but this has no index $x$?}

@@

	 &\langle n^{x}|d_{x}\otimes \dd|\xi^{x}\rangle\nonumber\\=&\langle n_{1}^{x},\ldots,n_{N}^{x}| (\exp{(E_{N1}^{x}+\ldots+E_{N\,N-1}^{x}}))^{T}R_{x}\otimes\sum_{q_{1}^{u(x)},\ldots,q_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{q_{a}^{u(x)}}\right)\langle q_{1}^{u(x)},\ldots,q_{N}^{u(x)}|\nonumber

@@

\sum_{q_{1}^{u(x)},\ldots,q_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{q_{a}^{u(x)}}\right)\langle q_{1}^{u(x)},\ldots,q_{N}^{u(x)}|\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle=\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}
\todo{what happens to $q_N$?}

@@

Taking the tensor product of both sides of \eqref{siteHadamardI} with 
\langle \rho|_{u(x)}=\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|_{u(x)}

@@

    	H_{x}^{T}d_{x}\otimes\langle\rho|_{u(x)}=

@@

|\alpha^{x}|\sum_{a=1}^{N-1}\left(\rho_{a}^{x}E_{Na}^{x}-E_{aa}^{x}\right)\otimes \langle\rho|_{u(x)}\dt

>>>>

Our strategy to solve for the non-equilibrium steady state is of a probabilistic nature and relies on the use of {\em duality} \cite{schutzSandow}. Starting from the pioneering work of Kipnis, Marchiorio and Presutti \cite{KMP}, this approach
has been substantially developed in recent years to study stochastic processes in the boundary-driven set-up \cite{giardina2009duality,carinci2013duality}.
The boundary-driven process is mapped to a dual process with absorbing extra sites and the problem of describing the stationary state of the original system
is reduced to the problem of computing the absorption probabilities of the dual particles. {\color{blue}On one hand, this absorbing duality allows to formally write the non-equilibrium steady state in a different (simpler) form. On the other hand, absorption probabilities are hard to to find since they fulfil multilinear algebraic equation with proper boundary conditions. The situation simplifies when the graph reduces to a chain with two reservoirs on the boundary sites. In this context, the integrable structure of the process can be combined with duality to compute non-equilibrium steady state. Recently, probabilistic techniques have been developped to compute absorption probabilities for the simple symmetric exclusion process \cite{floreani2023non}.}
{\color{red} Say that for a  general graph with boundaries attached to any site, this is a difficult task. }
% However,  for the case of integrable systems they can be computed exactly in closed-form.

@@

    \bm{\xi}=\left(\xi_{1}^{x},\ldots,\xi_{N}^{x},\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\right)_{x\in V}

@@

	 &\langle n^{x}_{1},\ldots,n_{N}^{x}|\left(d_{x}\otimes \dd\right)\left(|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle\otimes|\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle\right)\nonumber\\=&\langle n_{1}^{x},\ldots,n_{N}^{x}| (\exp{(E_{N1}^{x}+\ldots+E_{N\,N-1}^{x}}))^{T}R_{x}\otimes\sum_{q_{1}^{u(x)},\ldots,q_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{q_{a}^{u(x)}}\langle q_{1}^{u(x)},\ldots,q_{N}^{u(x)}|\nonumber

@@

\sum_{q_{1}^{u(x)},\ldots,q_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{q_{a}^{u(x)}}\langle q_{1}^{u(x)},\ldots,q_{N}^{u(x)}|\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle=\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}

@@

Taking the tensor product of both sides of \eqref{siteHadamardI}% with 
%\langle \rho|_{u(x)}=\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}%\right)^{\xi_{a}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|_{u(x)}

@@

    	&H_{x}^{T}d_{x}\otimes\left(\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|\right)\\=&

@@

|\alpha^{x}|\sum_{a=1}^{N-1}\left(\rho_{a}^{x}E_{Na}^{x}-E_{aa}^{x}\right)\otimes \left(\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|\right)
